### 2015-09-15 vmcai-2016-tex/intro.tex
Fixed another reference in the intro.

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates on a common set of data structure benchmarks for GSE evaluation~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015} an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure can overcome the cost of the solver calls. For the tree structures in the standard benchmarks, the
comparison shows an exponential increase in the number of heaps that
can be analyzed, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.

In summary, this paper presents a new initialization technique that
enables the use of guarded value sets in heap representations in a
sound and complete manner. Such a result means that any analysis using
this initialization technique can be assured of precision with regard
to \gsetxt{} semantics \cite{THINGSTHATBENEFIT}. This includes generating concrete heaps for test input generation.

>>>>

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates on a common set of data structure benchmarks for GSE evaluation~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015} an increase in the number of heaps that can be analyzed when compared to existing~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure can overcome the cost of the solver calls. For the tree structures in the standard benchmarks, the
comparison shows an exponential increase in the number of heaps that
can be analyzed, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.

In summary, this paper presents a new initialization technique called symbolic initialization that
enables the use of guarded value sets in heap representations in a
sound and complete manner. Such a result means that guarded 
value set-based analysis methods~\cite{Ferrara:2014,Torlak:2014,Sen:2014,Xie:2005,Dillig:2011,Yorsh:2008} can use symbolic initialization to be assured of precision with regard
to~\gsetxt{} semantics. This includes generating concrete heaps for test input generation.
